### 2023-02-09 documentation/paper.tex
Finish

@@

@@

\begin{itemize}
    \item Low sensitivity: Mobile cameras often have smaller sensors compared 
          to DSLR or mirrorless cameras, which can result in lower sensitivity 
          to light. This can make it difficult to capture usable images in low l
          ight conditions without using long exposures or high ISO values, 
          which can introduce noise and other artifacts.

@@

To address these constraints, several techniques can be used to improve the performance 
of mobile cameras in low light conditions. These include:

\begin{itemize}
    \item Noise reduction: Noise reduction algorithms can be used to reduce the noise 
          introduced by high ISO values or long exposures. These algorithms can smooth 
          out the image while preserving edges and other important details.

    \item High dynamic range techniques: HDR techniques, such as burst photography 
          and computational photography, can be used to extend the dynamic range of mobile 
          cameras and capture more detail in both the shadow and highlight areas of an image.

@@

The HDR+ image processing pipeline is a computational photography technique developed by Google for use 
in the Google Pixel smartphone. It is designed to capture high dynamic range images using 
burst photography. The algorithm uses computational techniques to extend the dynamic range 
of the captured images, rather than relying on multiple exposures as in traditional 
HDR techniques, in which a rapid sequence of images at different exposures is captured.
The captured images are merged to create a single HDR image. The HDR+ algorithm was developed 
to improve the quality and dynamic range of images captured on mobile devices, particularly in 
low-light conditions. The HDR+ algorithm consists of several steps, which are outlined in detail 
by Hasinoff et al. (2016) \cite{Hasinoff2016burst}. In brief, the steps are as follows:

@@

@@

To check how the HDR+ image processing pipeline described by Hasinoff et al. (2016) \cite{Hasinoff2016burst}
handles scenes under different lighting
conditions, an implementation of the pipeline should be made to work and applied to
different image bursts. The implementation used was developed by Timothy Brooks
\cite{Brooks2016git} and published as open source project.

>>>>

\subsection{Creating HDR images via exposure bracketing}
\label{sec:bracketing}

@@

\subsection{Challenges of photography with mobile devices}
\label{sec:challenges}

@@

\begin{itemize}
    \item Low sensitivity: Mobile cameras often have smaller sensors compared 
          to DSLR or mirrorless cameras, which can result in lower sensitivity 
          to light. This can make it difficult to capture usable images in low 
          light conditions without using long exposures or high ISO values, 
          which can introduce noise and other artifacts.

@@

\subsection{Addressing these challenges}
To address the constraints mentioned in \cref{sec:challenges}, several techniques 
from computational photography can be used to improve the quality of images captured 
captured mobile cameras \cite{delbracio2021mobile}. These include:

\begin{itemize}
    \item Noise reduction: Noise reduction algorithms can be used to reduce the noise 
          introduced by high ISO values. These algorithms can smooth 
          out the image while preserving edges and other important details.

    \item High dynamic range techniques: HDR techniques, such as burst photography, can be used to extend the dynamic range of mobile 
          cameras and capture more detail in both the shadow and highlight areas of an image.

@@

\subsection{HDR+ burst processing pipeline}
\label{sec:hdrpluspipeline}
The HDR+ image processing pipeline is a computational photography technique developed by Google for use 
in the Google Pixel smartphone. It is designed to capture high dynamic range images using 
burst photography. The algorithm uses computational techniques to extend the dynamic range 
of the captured images, rather than relying on multiple exposures as in traditional 
HDR techniques, in which a rapid sequence of images at different exposures is captured.
The captured images are merged to create a single HDR image. The HDR+ algorithm was developed 
to improve the quality and dynamic range of images captured on mobile devices, particularly in 
low-light conditions. The HDR+ algorithm consists of several steps, which are outlined in detail 
by Hasinoff et al. (2016) \cite{Hasinoff2016burst}. In brief, the steps are as follows:

@@

\subsection{Improvements and new approaches since HDR+}
\label{sec:newerstuff}

@@

To check how the HDR+ image processing pipeline described in \cref{sec:hdrpluspipeline}
handles scenes under different lighting
conditions, an implementation of the pipeline should be made to work and applied to
different image bursts. The implementation used was developed by Timothy Brooks
\cite{Brooks2016git} and published as open source project.
